\documentclass{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    citecolor=red,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}

\title{Evaluation of Pair Programming}

\author{ Praanto Samadder and Rushil Garg }

\begin{document}
\maketitle
\begin{abstract}
    This research paper aims to provide a comprehensive report on the effectiveness and efficiency of pair programming within an agile team setting. In more specific terms, it delves into the analysis of how pair programming functions in an agile team environment, particularly one that has a large scope for work parallelization. The analysis is grounded in personal accounts, offering a rich and detailed perspective on the practice. These personal accounts serve as the primary material for the study, allowing for a nuanced presentation of the findings. Moreover, the article goes beyond presenting these findings in isolation; it also compares them with outcomes from existing research on other agile teams, providing a broader context for understanding the results. Detailed methods of data collection are also outlined in the article, ensuring transparency and reproducibility of the research process. Additionally, the article is written from the unique perspectives of one developer and one scrum master, both of whom have firsthand experience working in the agile team under study. This dual perspective enriches the analysis, offering insights from different roles within the team and highlighting the collaborative nature of agile methodologies.
\end{abstract}

\textbf{\textit{Keywords}}: agile development, collaborative work, survey data analysis

\input{introduction}
\input{background}
\input{research_method}
\input{project_result}
\input{analyse}
\input{conclusion}

\begin{thebibliography}{1000}
    \bibitem{agile}
    Shamsulhuda Khan,
    A Comparative Study of Agile and Waterfall Software Development Methodologies, \textit{DOI: 10.48175/IJARSCT-5696}
    
    \bibitem{agile_3}
    Cockburn, Alistair, and Laurie Williams. "The costs and benefits of pair programming." \textit{Extreme programming examined 8 (2000): 223-247.}
    
    \bibitem{agile_2}
    Jordan B Barlow, et. al, Overview and Guidance on Agile Development in Large Organizations, \textit{Volume 29, Article 2, pp. 25-44, July 2011}



    \bibitem{pair}
    Nawrocki, Jerzy, and Adam Wojciechowski. "Experimental evaluation of pair programming." \textit{European Software Control and Metrics (Escom) (2001): 99-101.}

    \bibitem{pair_2}
    Joe E Hannay, The effectiveness of pair programming: A meta-analysis, \textit{DOI: 10.1016/j.infsof.2009.02.001}


    \bibitem{llama3}
    Meta, \href{https://ai.meta.com/blog/meta-llama-3/}{Introducing Meta Llama 3: The most capable openly available LLM to date}, last accessed May 16 2024 at 15:40

    \bibitem{skill_issue}
    Rinaily Bonifacio, \href{https://www.shiftbase.com/glossary/skills-gap}{The Skills Gap Challenge: Understanding and Overcoming It}, last accessed May 16, 2024 at 22:44

    \bibitem{team_building}
    Sadman Sakib Khan, \href{https://polygontechnology.io/benefits-of-having-an-agile-team-building-your-digital-product/}{Benefits Of Having An Agile Team Building Your Digital Product}

\end{thebibliography}

\end{document}